DisCon Children 6 vs. 1 exposure trials

### 2019-11-25 analysis/02_kids_600.Rmd
update repo to check analysis

---
title: "DisCon Children 6 exposure trials"
output: html_document
  code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(readxl)
library(knitr)

library(lsr)
library(pwr)

@@

raw_data <- raw_data %>%
  filter(subid != "190402_3_d600")

@@

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  mutate(subid = ifelse(subid == "190416_4_d6v1","190416_4_d600",subid))%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

```{r sanity checks}
# filtering out subjects that perform poorly on training trials
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

@@

@@

```{r}
data %>%
  group_by(subage
           #,sex
           )%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

@@

```{r proportion of choices}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

@@

Proportion correct choice by age continous

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)
```

@@

```
Plotting posterior based on t-test

```{r}
plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
  select(-correct)

@@

ggplot(plot_dens, aes(posterior, group = factor(age))) +
  geom_density(alpha = .5)+
  geom_vline(xintercept = 1/3, lty=2)+
  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
  labs(x="Proportion Correct")+
  theme_few() +
  xlim(-0.05,1.05)+
  guides(alpha = F)+
  scale_fill_solarized(name = "Age")+
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

# Comparison to chance based on model

```{r}
model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num))

@@

chance_model <- brm(correct_target1 ~ 1 + 
                      (1| subid) + (age_num | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
bayesplot::mcmc_areas(as.array(chance_model), pars = c("b_Intercept"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

# Model 
```{r, include = F}
library(brms)

model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num))

@@

kbm1 <- brm(correct_target1 ~ age_num +
                      (1| subid) + (age_num | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm1)
```

@@

```{r, include = F}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (age_num | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm2)
```

@@

```{r}
child_waic <- brms::WAIC(kbm1, kbm2, compare = F)

child_weights <- model_weights(kbm1, kbm2)

@@

```{r}
data_frame(
  model = c("kbm1_w_age","kbm2"),
  WAIC = c(child_waic$kbm1$estimates[3,1],child_waic$kbm2$estimates[3,1]),
  SE = c(child_waic$kbm1$estimates[3,2],child_waic$kbm2$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```

# Check category, position and trial

## category effects
```{r proportion of choices}
cat_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(target1,subid) %>%
  summarise(correct = mean(correct_target1))

@@

## position effects
```{r }
pos_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(n = n())%>%
  group_by(pickPos)%>%
  multi_boot_standard(col = "n")

@@

## trial effects
```{r proportion of choices}
trial_plot <- data %>%
  filter(phase == 'test')

@@

# one sample wilcoxon
```{r}

>>>>

---
title: "DisCon Children 6 exposure trials"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(readxl)
library(knitr)
library(brms)
library(lsr)
library(pwr)

@@

raw_data <- raw_data %>%
  filter(subid != "190402_3_d600")%>%
  mutate(subage = str_replace(subage," ",""))

@@

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  mutate(subid = ifelse(subid == "190416_4_d6v1","190416_4_d600",subid),
         subid = ifelse(subid == "190828_3_d500","190828_3_d600",subid))%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

```{r sanity checks, include = F}
# filtering out subjects that perform poorly on training trials
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

@@

```{r}
#clean data file for repo
data_ex1 <- data %>%
  filter(phase == "test")%>%
  mutate(correct = ifelse(correct_target1 == "1", 1, 0),
         target_category = target1, 
         picked_category = pickCat,
         experiment = "simple_inference", 
         id = paste0("part_",as.numeric(as.factor(subid))),
         id = paste(id, experiment, sep = "_"),
         speaker = agent,
         age_group = subage)%>%
  select(id, age_group,age_num,sex,experiment,trial,speaker,target_category, picked_category,correct)

write_csv(data_ex1, path="../data/data_ex1.csv")
```

@@

```{r}
data %>%
  group_by(subage
           #,sex
           )%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

@@

```{r}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

@@

```{r}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

@@

# Proportion correct choice by age continous

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "glm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)
```

@@

# Plotting posterior based on t-test

```{r, echo = F}
plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
  select(-correct)

@@

post_plot <- ggplot(plot_dens, aes(posterior, group = factor(age))) +
  geom_density(alpha = .5)+
  geom_vline(xintercept = 1/3, lty=2)+
  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
  labs(x="Proportion Correct")+
  theme_few() +
  xlim(-0.05,1.05)+
  guides(alpha = F)+
  scale_fill_ptol(name = "Age")+
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

post_plot
```

```{r, include = F, cache = T}
model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num))

@@

chance_model <- brm(correct_target1 ~ 1 + 
                      (1| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          silent = T, 
          refresh = 0, 
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r, include = F}
bayesplot::mcmc_areas(as.array(chance_model), pars = c("b_Intercept"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

# Model

## Model with age
```{r, cache = T}
model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num))

@@

kbm1 <- brm(correct_target1 ~ age_num +
                      (1| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm1)

waic1 <- waic(kbm1)
```
### Plotting model fixed effects

@@

## Model without age

```{r, cache = T}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F, 
          chains = 4, 
          cores = 4,
          save_all_pars = TRUE,
          iter = 5000)

summary(kbm2)

waic2 <- waic(kbm2)
```

@@

```{r}
child_weights <- model_weights(kbm1, kbm2)

@@

```{r}
data_frame(
  model = c("kbm1_w_age","kbm2"),
  WAIC = c(child_waic$loos$kbm1$waic,child_waic$loos$kbm2$waic),
  SE = c(child_waic$loos$kbm1$se_waic,child_waic$loos$kbm2$se_waic),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)

```{r , include = F}
cat_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(target1,subid) %>%
  summarise(correct = mean(correct_target1))

@@

```{r , include = F}
pos_plot <- data %>%
  filter(phase == 'test')%>%
  group_by(pickPos,subid) %>%
  summarise(n = n())%>%
  group_by(pickPos)%>%
  multi_boot_standard(col = "n")

@@

```{r , include = F}
trial_plot <- data %>%
  filter(phase == 'test')

@@

```{r, include = F}

### 2019-11-25 analysis/02_kids_6v1.Rmd
update repo to check analysis

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, distribution,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

p2 <- p1 %>%
  group_by(subage,distribution) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = distribution, y = correct, col = subage), alpha = .2 ,width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = subage),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

kbm1 <- brm(correct_target1 ~ age_num * distribution +
                      (distribution| subid) + (distribution | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num", "b_distribution6M0M0", "b_age_num:distribution6M0M0"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

```{r, include = F}
kbm2 <- brm(correct_target1 ~ age_num +
                      (distribution| subid) + (distribution | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

@@

## trial effects
```{r proportion of choices}
trial_plot <- data %>%
  filter(phase == 'test')

ggplot(data = trial_plot, aes(x = trial, y = correct_target1)) +
  geom_jitter(alpha = .2,width = .2,height = .01)+
  geom_smooth(method = "loess",  se = T, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

>>>>

```{r}
#clean data file for repo
data_ex2 <- data %>%
  filter(phase == "test")%>%
  mutate(correct = ifelse(correct_target1 == "1", 1, 0),
         condition = ifelse(distribution == "6-0-0", "high_input", "low_input"),
         target_category = target1, 
         picked_category = pickCat,
         experiment = "variable_input", 
         speaker = agent,
         id = paste0("part_",as.numeric(as.factor(subid))),
         id = paste(id, experiment, sep = "_"),
         age_group = subage)%>%
  select(id, age_group,age_num,sex,experiment,trial,condition, speaker, target_category, picked_category,correct)

write_csv(data_ex2, path="../data/data_ex2.csv")
```

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  group_by(experiment) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = experiment, y = correct, col = experiment), alpha = .2 ,width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper, col = experiment),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

kbm1 <- brm(correct_target1 ~ age_num * distribution +
                      (distribution| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4, 
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num", "b_distribution6M0M0", "b_age_num:distribution6M0M0"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```
```{r, include = F}
#   model

kbm2 <- brm(correct_target1 ~ age_num + distribution +
                      (distribution| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4, 
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r, include = F}
kbm3 <- brm(correct_target1 ~ age_num +
                      (distribution| subid),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4, 
          cores = 4, 
          save_all_pars = TRUE,
          iter = 2000)

summary(kbm3)
```

@@

## trial effects
```{r proportion of choices}
trial_plot <- data %>%
  filter(phase == 'test')5

ggplot(data = trial_plot, aes(x = trial, col = distribution,  y = correct_target1)) +
  geom_jitter(alpha = .2,width = .2,height = .01)+
  geom_smooth(method = "loess",  se = T, size = 1, alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  #facet_grid(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```
